Assessing primitives performance\\ on multi-stage execution

### 2018-05-18 paper.tex
consistency for llvm gcc names, add a sentence about the performance gap within llvm

\paragraph{Optimization potential on large strings comparison.}
The Plugin comes with an overhead due the use of an interface. Besides, cross-file inlining is not performed for plugin, like said in Section~\ref{sec:implem_cmp}. These are some of the factors explaining the performance gap between these versions and the \legSlang and \legRTL ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the Slang implementation when strings of 100 characters are compared: Slang is 17.7 times faster than Baseline while Slang+JIT is 18,6 times faster than Baseline. 
This last observation only applies to the \GCCLinux results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.

\paragraph{Control over generated code.} One could notice a rather striking performance difference between the 2 compilers: when compiling with GCC, the performance between the \legSlang and \legRTL implementations is really close for long strings (100 characters and longer), with respectively 25,42 and 26,76 relative speed-up factors for a 1000-characters string. Yet performance greatly differs when LLVM is used, with respectively 10,67 and 25,4 relative speed-up factors.

This difference is mainly due to the optimizations performed by both the compilers: as depicted in Figure~\ref{fig:Asm}, GCC generates instructions that are very close to the ones generated by the JIT, hence the similar speed-up factors. On the contrary, LLVM generates more instructions: it especially fails at preserving registers holding the strings (edi and esi), leading to two extra instructions (bolded in the figure) that  load the strings at each iteration.

One can also notice the gap between the Plugin and Slang implementations in LLVM, which does not appear in GCC. \sk{one last comment: WHY?!}

In this section, we compared the performance of the different implementations against a baseline (\emph{i.e.,}{pure Smalltalk code}) implementation. The results showed the \legRTL implementation was always the fastest. Otherwise, most of the performance gaps between the primitive versions could be explained by 3 criteria: stack swithing, optimization for large strings, and the control over generated code.

>>>>

\paragraph{Optimization potential on large strings comparison.}
The Plugin comes with an overhead due the use of an interface. Besides, cross-file inlining is not performed for plugins, like said in Section~\ref{sec:implem_cmp}. These are some of the factors explaining the performance gap between these versions and the \legSlang and \legRTL ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the Slang implementation when strings of 100 characters are compared: Slang is 17.2 times faster than Baseline while Slang+JIT is 18,6 times faster than Baseline. 
This last observation only applies to the \GCCLinux results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.

\paragraph{Control over generated code.} One could notice a rather striking performance difference between the 2 compilers: when compiling with GCC, the performance between the \legSlang and \legRTL implementations is really close for long strings (100 characters and longer), with respectively 22.54 and 24.93 relative speed-up factors for a 1000-characters string. Yet performance greatly differs when LLVM is used, with respectively 12,94 and 24,88 relative speed-up factors.

This difference is mainly due to the optimizations performed by both the compilers: as depicted in Figure~\ref{fig:Asm}, \GCCLinux generates instructions that are very close to the ones generated by the JIT, hence the similar speed-up factors. On the contrary, \LLVMMac generates more instructions: it especially fails at preserving registers holding the strings (edi and esi), leading to two extra instructions (bolded in the figure) that  load the strings at each iteration.

One can also notive a significant gap between the Plugin and Slang implementations in \LLVMMac. This can also be explained by a difference in optimizations. As seen in Figure \ref{fig:Asm}, the comparison loop is indeed optimized in the Plugin version and is similar to the JIT implementation.

In this section, we compared the performance of the different implementations against a baseline (\emph{i.e., }{pure Smalltalk code}) implementation. The results showed the \legRTL implementation was always the fastest. Otherwise, most of the performance gaps between the primitive versions could be explained by 3 criteria: stack swithing, optimization for large strings, and the control over generated code.
